---
title: "Economic Dashboard"
author: "Daniel Lee"
date: '2022-05-02'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE, 
    message = FALSE, 
    warning = FALSE,
    fig.align = "center"
    )

# Set up

# Core
library(tidyverse)
library(tidyquant)

# FRED data
library(eFRED)

# Time series
library(timetk)

# Interactive visualization
library(plotly)

api_key <- "11c92c9630cc2c5c83eb5da3b01a59f0"
set_fred_key(api_key)

# Load functions
source("../00_scripts/plot_Tseries_with_us_recessions.R")
source("../00_scripts/wrangle_plot_overall_and_industry_gdp.R")

# Import Data
market_indicators_fig   <- read_rds("../00_data/fig/market_indicators_fig.rds")
economic_indicators_fig <- read_rds("../00_data/fig/economic_indicators_fig.rds")
industry_indicators_fig <- read_rds("../00_data/fig/industry_indicators_fig.rds")
```

# {.tabset .tabset-fade}

## Market Indicators

```{r}
ggplotly(market_indicators_fig)

```

## Economic Indicators

```{r}
ggplotly(economic_indicators_fig)
```


## Industry Indicators
Overall U.S. Economy versus Individual Industry

How sensitive is your industry to the overall economy? Is it more or less volatile? If less volatile, you may not be so much worry about a recession. In addition, does it lead or lag the overall economy? Changes in the overall economy may help you navigate economic cycles.

```{r fig.height=10, fig.width=10}
ggplotly(industry_indicators_fig) %>%
    
    layout(legend = list(
        orientation = "h",
        x = 0.25))
```

Year-Over-Year Percent Change

NAICS Sector (2-digit code)
