---
title: "Econometer: Radar for Business"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: column
    vertical_layout: fill
---

```{r setup, include=FALSE}
# Shiny
library(shiny)
library(flexdashboard)

# Core
library(tidyverse)
library(tidyquant)

# Timeseries
library(lubridate)
library(timetk)

# Interactive visualization
library(plotly)

# FRED data
library(eFRED)

api_key <- "11c92c9630cc2c5c83eb5da3b01a59f0"
set_fred_key(api_key)

# Load functions
# Load the function in the local environment using local = TRUE to find Recession_Dates_tbl
source("../00_scripts/plot_Tseries_with_us_recessions.R", local = TRUE)
source("../00_scripts/wrangle_plot_overall_and_industry_gdp.R")

# Import Data
# Market Indicators 
VIX_tbl                <- read_rds("../00_data/VIX_tbl.rds")
Treasury10_Yield_tbl   <- read_rds("../00_data/Treasury10_Yield_tbl.rds")
Yield_Spread_tbl       <- read_rds("../00_data/Yield_Spread_tbl.rds")
Home_Price_tbl         <- read_rds("../00_data/Home_Price_tbl.rds")

# Economic Indicators - US
Recession_Dates_tbl    <- read_rds("../00_data/Recession_Dates_tbl.rds")
Inflation_tbl          <- read_rds("../00_data/Inflation_tbl.rds")
Unemployment_Rate_tbl  <- read_rds("../00_data/Unemployment_Rate_tbl.rds")
GDP_Growth_tbl         <- read_rds("../00_data/GDP_Growth_tbl.rds")
Consumer_Sentiment_tbl <- read_rds("../00_data/Consumer_Sentiment_tbl.rds")

# Industry
realGDP_states_q_NAICS_tbl <- read_rds("../00_data/realGDP_states_q_NAICS_tbl.rds")
```



Column {.sidebar data-width=300}
-----------------------------------------------------------------------

```{r}
shinyWidgets::pickerInput(
  inputId = "industry", 
  label = "Select State", 
  choices = unique(realGDP_states_q_NAICS_tbl$place %>% sort()), 
  options = list(
    `actions-box` = TRUE, 
    size = 10,
    `selected-text-format` = "count > 3"
  ), 
  multiple = FALSE
)

shinyWidgets::pickerInput(
  inputId = "industry", 
  label = "Select Industry", 
  choices = unique(realGDP_states_q_NAICS_tbl$NAICS_desc %>% 
                       str_trunc(width = 30, side = "right")), 
  options = list(
    `actions-box` = TRUE, 
    size = 10,
    `selected-text-format` = "count > 3"
  ), 
  multiple = FALSE
)

br()
hr()
br()

actionButton("go", "Submit")
```


Column {data-width=700 .tabset .tabset-fade}
-----------------------------------------------------------------------

### Markets

```{r}
# Display all indicators using facet_wrap()


VIX_tbl %>% plot_Tseries_with_us_recessions(title = "The Chicago Board Options Exchange Volatility Index", 
                                            yaxis_title = "Percent")

Treasury10_Yield_tbl %>% plot_Tseries_with_us_recessions(title = "10-YR Treasury Yield",
                                                         yaxis_title = "Percent")

Yield_Spread_tbl %>% plot_Tseries_with_us_recessions(title = "Treasury Yield Spread between the 10 Year Note and the 3 Month Bill",
                                                     yaxis_title = "Percent")

Home_Price_tbl %>%

    # Calculate year-over-year change
    mutate(value = (value/lag(value, n = 12)-1)*100) %>%

    # Plot
    plot_Tseries_with_us_recessions(title = "S&P/Case-Shiller 20-City Composite Home Price Index",
                                    yaxis_title = "Year-Over-Year Percent Change")
```


### Economy

```{r}

```

### Industry

```{r}

```

### Other considerations

Producers of intermediate goods should watch consumption of the goods that use their product. A wheat farmer needs to watch bread sales.

A company should monitor its own customers. A wheat farmer needs to watch flour sales. 

Pay a close attention to raw material prices if you are a manufacturer, utility, contractor with significant exposure to one or two raw materials.

A manager should assess risk of a regional recession if the company:

* sells into a local market distinct from the national economy. 
* produces in a distinct local market and sell into a national or global market.

A company in capital-intensive industries (e.g., real estate, mining, and utilities) should monitor the industry's capital investment. 



```{r}
### Options to consider when managing through the recession



# When expecting a downturn


# During a moderate downturn


# During a severe recession


# During a recovery


# During a boom


# Add identifying opportunities
```






